%-------------------------
% Jake's Resume Template
% Upload this file to Overleaf: https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% Or compile locally with pdflatex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Viral Shastri} \\ \vspace{1pt}
    \small +91 84692 23098 $|$
    \href{mailto:viralshastri99@gmail.com}{\underline{viralshastri99@gmail.com}} $|$
    \href{https://linkedin.com/in/viralshastri19}{\underline{linkedin.com/in/viralshastri19}} $|$
    Pune, Maharashtra, India
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Backend engineer with 4.5 years of experience designing and owning high-throughput distributed systems. Built Hyper-Y from scratch as the sole engineer at AVRL — a real-time freight pricing engine processing 100+ requests/sec across 8 enterprise TMS integrations. Expert in Python and event-driven pipeline architecture. Experienced with Node.js across internal tooling and freelance projects. Thrive in high-ownership, small-team environments solving complex backend problems end-to-end.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, Node.js} \\
     \textbf{Backend}{: Flask, RESTful API Design, Event-Driven Architecture, Microservices, Serverless} \\
     \textbf{Databases}{: PostgreSQL, Redis, NoSQL, Google Cloud Storage} \\
     \textbf{Cloud \& DevOps}{: GCP, Google App Engine, GitHub Actions, CI/CD, Git} \\
     \textbf{Frontend}{: React.js, Next.js (working knowledge)} \\
     \textbf{Practices}{: Agile, Cross-functional Collaboration}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AVRL}{Austin, Texas, USA (Remote)}
      {Primary Product Engineer --- Hyper-Y}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{Designed and built Hyper-Y from scratch as sole engineer (reporting to CTO) --- a high-availability freight pricing engine processing \textbf{100+ req/sec} across \textbf{8 enterprise TMS integrations} (BlueYonder, MercuryGate, Navisphere, UberFreight, E2Open) on GCP.}
        \resumeItem{Architected a multi-stage event-driven microservices pipeline --- BNB bid/no-bid evaluation, Phoenix Pricing Engine, and Premium Adjustments via chained decision trees --- enabling per-carrier bidding rules through configuration rather than code deployments.}
        \resumeItem{Built 8 enterprise TMS integration adapters each handling platform-specific authentication, schema normalization, and automated bid submission using Python and RESTful APIs.}
        \resumeItem{Deployed and operates Hyper-Y on Google App Engine (serverless) with a private GitHub Actions CI/CD pipeline; designed the authentication service and structured observability pipeline logging all bid decisions to GCP Datastore.}
        \resumeItem{Built multiple internal Node.js tooling applications automating day-to-day operational workflows across the AVRL team.}
      \resumeItemListEnd

    \resumeSubheading
      {AVRL}{Austin, Texas, USA (Remote)}
      {RPA Automation Engineer}{2020 -- 2023}
      \resumeItemListStart
        \resumeItem{Built RPA bot suite in JavaScript and Electron automating the full carrier bidding lifecycle --- bots navigated TMS interfaces, extracted shipment details, routed data through AVRL's pricing pipeline, and placed bids autonomously for large US freight carriers.}
        \resumeItem{Automated a previously manual, error-prone bidding process across multiple enterprise TMS platforms, eliminating all manual data entry for US carrier operations teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Computer Applications (MCA)}{2022}
      {[Your University Name]}{Pune, Maharashtra}
    \resumeSubheading
      {Bachelor of Computer Applications (BCA)}{2019}
      {[Your University Name]}{[City], Maharashtra}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
